---
title: "lab 16-01-2020"
author: "Aruna vijayan"
date: "16/01/2020"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```



```{r}
View(iris)
```

injecting missing values to the original dataset
```{r}
set.seed(86)

iris[sample(1:nrow(iris), 5), "Sepal.Width"] <- NA

iris[sample(1:nrow(iris), 10), "Petal.Length"] <- NA

iris[sample(1:nrow(iris), 8), "Sepal.Length"] <- NA
```

view the missing values in the original dataset
```{r}
View(iris)
```
how to identify the missing values
```{r}
is.na(iris)
```
function to get percentage of missing value
```{r}
nrow(iris[!complete.cases(iris), ])/nrow(iris)*100
```
interpretation :
we can calculate the persentage of null values that are presented in the iris dataset.

q.identify which variables and what percentage of observations from
each variable are missing.
```{r}
library(mice)
```
```{r}
install.packages("mice")
```
```{r}
md.pattern(iris)
```





Replacing the missing values(NA or others) using different methods 
one of those method is by Using impute function from Hmisc package,
```{r}
install.packages("Hmisc")
```
```{r}
library(Hmisc)
```

removing the missing values using Hmisc package
method 1:

```{r}
impute(iris$Sepal.Length, mean)
```
interpretation: this replacement is done using the null values are replaced using the mean values.

method 2:

```{r}
impute(iris$Sepal.Length, median)
```
interpretation:
in this method we replace the null values by median value.

when the mice function from the package it automatically detects the variables which have missing values.
Once detected, the missing values are then replaced by Predictive Mean Matching (PMM), this is a default method.
```{r}
imputed_iris <- mice(iris, m=5, method = 'pmm', seed = 101)
imputed_iris
```
interpretation:
imputing the missing values using mice,which will defaultly detect the missing values and replace it.
```{r}
summary(imputed_iris)
```
interpretation:
summary of all the imputed null values using mice.

checking for the imputed values,
```{r}
imputed_iris$imp
```

we can also use machine learning algorithms to checking and replace or remove the missing values in the given data set.
such methods are:

```{r}
iris <- iris[complete.cases(iris), ]
iris <- na.omit(iris)
iris
```
interpretation: deleted all the null values that are presented in our dataset.

injecting null values again;

```{r}
set.seed(86)

iris[sample(1:nrow(iris), 5), "Sepal.Width"] <- NA

iris[sample(1:nrow(iris), 10), "Petal.Length"] <- NA

iris[sample(1:nrow(iris), 8), "Sepal.Length"] <- NA

iris
```

```{r}
install.packages("bnstruct")
```

```{r}
library(bnstruct)
iris=as.data.frame(lapply(iris, as.numeric))
iris
```
using KNN classification method:
```{r}
library(VIM)
df23=kNN(iris,variable=("Sepal.Length"),k=5)
df23$Sepal.Length_impute=NA
df23$Sepal.Width_impute=NA
df23
```
```{r}
knn.impute(iris, k = 4, cat.var = 1:ncol(iris), to.impute = 1:nrow(iris), using = 1:nrow(iris))
```
```{r}
nrow(iris)
```
```{r}
get_numbers <- function(iris) {
    iris[toupper(iris) != tolower(iris)] <- NA
    return(as.double(as.character(iris)))
}
get_numbers
```
```{r}
iris=as.data.frame(lapply(iris, as.double))
iris
```

