---
title: "lab20-11-2019"
author: "Aruna vijayan"
date: "20/11/2019"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

1.Import the dataset data_marketing_budget_mo12 and do the exploratory data analysis.
```{r}
library(dplyr)
library(lattice)
library(ggplot2)
```
```{r}
markettingbudget <- read.csv("C:/Users/aruna/Downloads/data-marketing-budget-12mo.csv")
markettingbudget
```
2.Use Scatter Plot To Visualise The Relationship
```{r}
plot=ggplot(markettingbudget, aes(x = Spend, y = Sales)) +geom_point()
plot
```
INTERPRETATION:

From the scatter plot we can observe a linear relationship between the sales and spend. We
can observe that when the spend increases the sales also increases. Therfore Sales is the
dependent and spend is the independent variable.

3.Using BoxPlot To Check For Outliers
```{r}
name=c("Spend","Sales")
boxplot(markettingbudget$Spend,markettingbudget$Sales,main="Spend vs Sales")
```
INTERPRETATION:

From the above boxplot we could't find the outliers therefore the values are close to others.


4. Using Density Plot To Check If Response Variable Is Close To Normal
```{r}
plot(density(markettingbudget$Sales))
```
INTERPRETATION:

The response variable Sales is approximately close to normal distribution as the density
plot shows a bell shaped structure.


4. Check the Correlation Analysis



```{r}
cor(markettingbudget$Spend, markettingbudget$Sales)
```
```{r}

```
INTERPRETATION:
From the correlation analysis we obtained that the correlation value is 0.99 and it is highly
positively correlated and the degree of linear independence is high. Increase or decrease in
Spend has a siginificant effect on Sales.


5. Build the Linear Regression Model
```{r}
lmodel=lm(Sales~ Spend,data = markettingbudget)
lmodel
```
7.Capture the summary of the linear model
```{r}
summary(lmodel)
```

INTERPRETATION:

Null Hypothesis: Not statistically significant Alt Hypothesis: Statistically significant The p
value obtained is 1.707e-14 which is clearly less than the significant value 0.05 therefore
we are rejectin the null hypothesis and the linear regression model is statistically
siginificant.
```{r}
summary(lmodel)
```

INTERPRETATION:
The summary which gives all the statistical  details of the data.



```{r}
par(mfrow = c(2,2))
plot(lmodel)
```
INTERPRETATION:

1. Residuals vs Fitted: The first plot (residuals vs. fitted values) is a simple scatterplot
between residuals and predicted values. We can observe that it is less randomness
between the residual and fitted values.Therfore we can say that there is a linear
relationship between the response and outcome.The model data are simulated in a way
that meets the regression assumptions very well.
2. Normal Q-Q: This plot shows if residuals are normally distributed and from the plot
we can see that the residuals are normally distributed.
3. Scale-Location: It’s also called Spread-Location plot. This plot shows if residuals are
spread equally along the ranges of predictors. This is how you can check the
assumption of equal variance. In this case the residuals appears to be randomely
spread.Therefore we can say that the residuals are spread equally among the predictor
variables.

4. residual Vs Leverage This is used to find the influence of the variables. here be can see
the cook line only little therefore the residulas are inside the cooks line with only a
little influence.
