---
title: "Course Work"
author: "Aruna Vijayan"
date: '2022-06-23'
output: word_document
---
```{r}
##importing common packages
library(ggplot2)
library(tidyverse)
library(dplyr)
###importing  date and time series packages
library(lubridate)
library(tseries)
library(car)
```


```{r}
###importing input ,output signal  and time data
input_data <- read.csv("C:/Users/Admin/Documents/Course Work/course work 1/X.csv",header = TRUE)
output_data <- read.csv("C:/Users/Admin/Documents/Course Work/course work 1/y.csv")
times_data <- read.csv("C:/Users/Admin/Documents/Course Work/course work 1/time.csv")
```

combaining  output signal  and input signal

```{r}

full_data <-cbind(input_data,output_data)
full_data
```
converting data to time series,with interval of 10 secs

```{r}
 
timeseries <- ts(full_data,end=20,frequency = 10,start = 0.1)
head(timeseries)
```
converting the time series data to dataframe structure
selecting column y,x2, x1 ,
filtering values for x2= 0 i.e neutral audio
time series plotting 

```{r}
timeseries_data0 <-as.data.frame(timeseries)%>%filter(x2=='0')%>%ts(start = 0.1,end=10,frequency = 10) %>% plot(type='b',col='blue',main='timeseries pot of input signal and output signal')
timeseries_data0
```
converting the time series data to dataframe structure
selecting column y,x2, x1 ,
filtering values for x2= 1 i.e emotional audio
time series ploting 

```{r}
timeseries_data1 <-as.data.frame(timeseries)%>%filter(x2=='1')%>%ts(start = 10.1,end=20,frequency = 10) %>% plot(type='b',col='blue',main='timeseries pot of input signal and output signal')
timeseries_data1
```


```{r}

distribution0=as.data.frame(timeseries)%>%
  filter(x2=='0')%>% ##filtering values for x2== 0,neutral audio
  select(y,x1)#selecting column y x1 , input signal,output signal
```

```{r}
distribution0
```


```{r}
distribution1=as.data.frame(timeseries)%>%
  filter(x2=='1')%>% ##filtering values for x2== 1,emotional audio
  select(y,x1)#selecting column y x1 , input signal,output signal
distribution1
```
```{r}
par(mfrow=c(2,1))
hist(distribution0$y,xlab = 'output',main = ' histogram of input_signal',col = 'purple')
hist(distribution0$x1,xlab = 'input',main = ' histogram of input_signal',col = 'black')
par(mfrow=c(1,1))
```



```{r}

par(mfrow=c(2,1))
hist(distribution1$y,xlab = 'output',main = ' histogram of output_signal',col = 'purple')
hist(distribution1$x1,xlab = 'input',main = ' histogram of input_signal',col = 'black')
par(mfrow=c(1,1))
```

```{r}
hist(full_data$y,xlab = 'output data',main = ' histogram of input_signal',col = 'green')
```

```{r}
########correlationship
library(corrplot)
correlation0 <- cor(distribution0)
corrplot::corrplot(corr =correlation0,bg = "red",method = "pie",
                   title = " correlation plot of input and output signal")
```

```{r}
corrplot(cor(distribution0),method = "square",type = "upper",t1.col="black",t1.cex=2,col = colorRampPalette(c("purple","dark green"))(200))
```

```{r}
corrplot.mixed(cor(distribution0),upper = "square",lower = "number",addgrid.col="black",t1.col="black")
```

```{r}
corrplot.mixed(cor(distribution0),upper = "pie",lower = "number",addgrid.col="black",t1.col="black")
```


```{r}
cor(distribution0)
```

```{r}
correlation1 <- cor(distribution1)
corrplot::corrplot(corr =correlation1,bg = "red",method = "pie",
                   title = " correlation plot of input and output signal")
```

```{r}
cor(distribution1)
```

```{r}
corrplot.mixed(cor(distribution1),upper = "square",lower = "number",addgrid.col="black",t1.col="black")
```


```{r}
#scatterplot of distribution0
distribution0 %>% plot(type='p',main ='scatter plot of input signaland output signal  ',col = 'red',xlab='input_signal',ylab='output_signal')


```

```{r}
#####scatter plot
distribution1 %>% plot(type='p',main ='scatter plot of input signaland output signal  ',col = 'blue',xlab='input_signal',ylab='output_signal')
```

```{r}
###boxplot
boxplot(full_data$y,main ='box plot of output signal  ',col = 'red',ylab='output_sgnal')
```

```{r}
boxplot(distribution0$y,main ='box plot of output signal  ',col = 'red',ylab='output_sgnal')
```

```{r}
boxplot(distribution1$y,main ='box plot of output signal  ',col = 'red',ylab='output_sgnal')
```



Task 2 : Regression
2.1

```{r}
regression_data <- as.data.frame(full_data)
regression_data
```


```{r}

#models
#input values
value_1=regression_data$x1
value_2=regression_data$x1^2
value_3=regression_data$x1^3
value_4=regression_data$x1^4
value_5=regression_data$x1^5

```

```{r}
#values of x2
input_x2=regression_data$x2
```

```{r}
output=as.matrix(output_data)
head(output)
```

model 1
```{r}

reg_model_1 <-data.frame(input0=c(1),value_3,value_5,input_x2)#creating a dataframe for model 1
reg_mdl_1 <- as.matrix(reg_model_1)##converting dataframe to matrix
head(reg_mdl_1)
regmodel_1 <- solve(t(reg_mdl_1)%*%reg_mdl_1)%*%t(reg_mdl_1)%*%output#estimating the values of parameters using the list square method
head(regmodel_1)
```
Model 2

```{r}
reg_model_2 <-data.frame(input0=c(1),value_1,input_x2)#creating a dataframe for model 2
reg_mdl_2 <- as.matrix(reg_model_2)##converting dataframe to matrix
head(reg_mdl_2)
regmodel_2 <- solve(t(reg_mdl_2)%*%reg_mdl_2)%*%t(reg_mdl_2)%*%output#estimating the values of parameters using the list square method
head(regmodel_2)
```
model 3
```{r}
reg_model_3 <-data.frame(input0=c(1),value_1,value_2,value_4,input_x2)#creating a dataframe for model 3
reg_mdl_3 <- as.matrix(reg_model_3)##converting dataframe to matrix
head(reg_mdl_3)
regmodel_3 <- solve(t(reg_mdl_3)%*%reg_mdl_3)%*%t(reg_mdl_3)%*%output#estimating the values of parameters using the list square method
head(regmodel_3)
```
model 4
```{r}
reg_model_4 <-data.frame(input0=c(1),value_1,value_2,value_3,value_5,input_x2)#creating a dataframe for model 4
reg_mdl_4 <- as.matrix(reg_model_4)##converting dataframe to matrix
head(reg_mdl_4)
regmodel_4 <- solve(t(reg_mdl_4)%*%reg_mdl_4)%*%t(reg_mdl_4)%*%output#estimating the values of parameters using the list square method
head(regmodel_4)
```

model 5
```{r}
reg_model_5 <-data.frame(input0=c(1),value_1,value_3,value_4,input_x2)#creating a dataframe for model 5
reg_mdl_5 <- as.matrix(reg_model_5)##converting dataframe to matrix
head(reg_mdl_5)
regmodel_5 <- solve(t(reg_mdl_5)%*%reg_mdl_5)%*%t(reg_mdl_5)%*%output#estimating the values of parameters using the list square method
head(regmodel_5)
```
Task 2.2

model 1 residual_1
```{r}

residual_1 <- norm((output-(reg_mdl_1%*%regmodel_1))^2)
residual_1

```
model 2 residual_2
```{r}
residual_2 <- norm((output-(reg_mdl_2%*%regmodel_2))^2)
residual_2
```
model 3 residual_3
```{r}
residual_3 <- norm((output-(reg_mdl_3%*%regmodel_3))^2)
residual_3
```
model 4 residual_4

```{r}
residual_4 <- norm((output-(reg_mdl_4%*%regmodel_4))^2)
residual_4
```
model 5 residual_5

```{r}
residual_5 <- norm((output-(reg_mdl_5%*%regmodel_5))^2)
residual_5
```
TASK2.3 LOGlikehood function##########################

loglikehood 1
```{r}
loglike_1 <- -(nrow(output)/2*log(2*pi))-(nrow(output)/2*(log(residual_1/(nrow(output)-1))))-residual_1*(1/(2*(residual_1/(nrow(output)-1))))
head(loglike_1)
```
```{r}
#loglikehood 2
loglike_2 <- -(nrow(output)/2*log(2*pi))-(nrow(output)/2*(log(residual_2/(nrow(output)-1))))-residual_2*(1/(2*(residual_2/(nrow(output)-1))))
loglike_2
```

```{r}
#loglikehood 3
loglike_3 <- -(nrow(output)/2*log(2*pi))-(nrow(output)/2*(log(residual_3/(nrow(output)-1))))-residual_3*(1/(2*(residual_3/(nrow(output)-1))))
loglike_3
```

```{r}
#loglikehood 4
loglike_4 <- -(nrow(output)/2*log(2*pi))-(nrow(output)/2*(log(residual_4/(nrow(output)-1))))-residual_4*(1/(2*(residual_4/(nrow(output)-1))))
loglike_4
```


```{r}

#loglikehood 5
loglike_5 <- -(nrow(output)/2*log(2*pi))-(nrow(output)/2*(log(residual_5/(nrow(output)-1))))-residual_5*(1/(2*(residual_5/(nrow(output)-1))))
loglike_5
```
TASK 2.4 AIK AND BIC  aikek information criterion/bayesian information criterion
k=number of parameter estimated

model 1 AIK AND BIC
```{r}
length(regmodel_1)
length(regmodel_2)
length(regmodel_3)
length(regmodel_4)
length(regmodel_5)
```


```{r}

k1=4
data_AIC_1 <- 2*k1-(2*loglike_1)
data_AIC_1
data_BIC_1 <- k1*log(nrow(output))-(2*(loglike_1))
data_BIC_1


```

```{r}
#model 2 AIC AND BIC
k2=3
data_AIC_2 <- 2*k2-(2*loglike_2)
data_AIC_2
data_BIC_2 <- k2*log(nrow(output))-(2*(loglike_2))
data_BIC_2


```

```{r}
#model 3 AIC AND BIC
k3=5
data_AIC_3 <- 2*k3-(2*loglike_3)
data_AIC_3
data_BIC_3 <- k3*log(nrow(output))+(2*(loglike_3))
data_BIC_3

```

```{r}

#model 4 AIC AND BIC
k4=6
data_AIC_4 <- 2*k4-(2*loglike_4)
data_AIC_4
data_BIC_4 <- k4*log(nrow(output))+(2*(loglike_4))
data_BIC_4

```

```{r}

#model 5 AIC AND BIC
k5=5
data_AIC_5 <- 2*k5-(2*loglike_5)
data_AIC_5
data_BIC_5 <- k5*log(nrow(output))+(2*(loglike_5))
data_BIC_5
```
```{r}
error1=(output-(reg_mdl_1%*%regmodel_1))
head(error1)
```

```{r}
error2=(output-(reg_mdl_2%*%regmodel_2))
head(error2)
```

```{r}
error3=(output-(reg_mdl_3%*%regmodel_3))
head(error3)
```

```{r}
error4=(output-(reg_mdl_4%*%regmodel_4))
head(error4)
```

```{r}
error5=(output-(reg_mdl_5%*%regmodel_5))
head(error5)
```

```{r}
qqnorm(error1)
qqline(error1, col = 2)

```
residuals tend to stray from the line quite a bit near the tails, which could indicate that they’re not normally distributed.

```{r}
qqnorm(error2)
qqline(error2, col = 2)

```

```{r}
qqnorm(error3)
qqline(error3, col = 2)
```

```{r}
qqnorm(error4)
qqline(error4, col = 2)
```

```{r}
qqnorm(error5)
qqline(error5, col = 2)
```


```{r}
set.seed(123)
same_data<-sample(1:200,140) #Taking sample of 140 rows
head(same_data)

```


```{r}
train_data<-regression_data[same_data,]
head(train_data)

```


```{r}
test_data<-regression_data[-same_data,]
head(test_data)
```

```{r}
splitted_data<-data.frame(input0=c(1),train_data$x1,train_data$x1^2,train_data$x1^4,train_data$x2)
split_data<- as.matrix(splitted_data)
head(split_data)
```

```{r}
y_out<-train_data$y
y_out<-as.matrix(y_out)
```

```{r}
rr_model<-solve(t(split_data)%*%split_data)%*%t(split_data)%*%y_out
rr_model
```
```{r}
sum_split<-sum(split_data)/length(y_out)
sum_split
```

```{r}
prediction<-sum_split*test_data
head(prediction)
```

```{r}
square_root<-sqrt(var(prediction$y))
square_root
```

```{r}
mean_predict<-mean(prediction$y)
mean_predict
```

```{r}
paste('Confidence Interval',mean_predict-1.96*square_root/sqrt(nrow(test_data)),mean_predict+1.96*square_root/sqrt(nrow(test_data)))
std1<-sqrt(var(prediction$x1))
std1
```

```{r}
mean_value<-mean(prediction$x1)
mean_value
```

```{r}
paste('Confidence Interval',mean_value-1.96*std1/sqrt(nrow(test_data)),mean_value+1.96*std1/sqrt(nrow(test_data)))
```

```{r}
the_error<-test_data$y-prediction$y
head(the_error)
error_rate<-test_data$y+prediction$y
head(error_rate)
```

```{r}
lower_bound<-the_error
upper_bound<-error_rate
predict_test_out<-test_data$y
```

```{r}
prediction %>% ggplot(aes(x1,y))+geom_errorbar(ymin=lower_bound,ymax=upper_bound)+ geom_point(aes(x1),col='Red') +geom_point(aes(x1,predict_test_out),col='Yellow')+ggtitle('Confidence Error Bar Plot')+theme(plot.title = element_text(hjust = 0.5))+xlab('Input Data Set') + ylab('Output Data Set')
```

```{r}

```

